---
title: "p8105_hw1_ym2183"
author: "Anna Ma"
date: "9/26/2021"
output: github_document
---

## Problem 1

```{r, include=FALSE}
library(tidyverse)
```


### 1.1 Creating the Data frame
```{r}
problem1_df <- tibble(
  vec_random = rnorm(10, mean = 0, sd = 1),
  vec_logical = vec_random > 0, 
  vec_char = c("a","b","c","d","e","f","g","h","i","j"),
  vec_factor = factor(c("low","medium","high","medium","high","low","low","medium","high","high"))
)
```

### 1.2 Take mean of each variable
```{r}
#1.Random sample of standard normal distribution 
mean(pull(problem1_df,vec_random))
#2.Logical vector
mean(pull(problem1_df,vec_logical))
#3. Character vector
mean(pull(problem1_df,vec_char))
#4. Factor Vector 
mean(pull(problem1_df,vec_factor))
```
We can take the mean for the random sample of standard normal distribution and the logical vector. However, the mean of the character vector and factor vector cannot be taken. 

### 1.3
```{r, eval=FALSE}
#1.Logical vector
as.numeric(pull(problem1_df,vec_logical))
#2. Character vector
as.numeric(pull(problem1_df,vec_char))
#3. Factor Vector 
as.numeric(pull(problem1_df,vec_factor))
```
The logical vector and the factor vector was converted. In the logical vector, TURE values are converted to 1, and the FALSE values are converted to zero. In the factor vector, the levels were converted to numeric value 1 to 3 indicating 3 different levels. The character vector was not converted to numbers. This explain why the logical vector has a mean whereas the other vectors does not. The mean of the the logical vector shows the average of the sample and how likely the sample is true; the character values do not have intrinsic numeric value and therefore does not have a mean; finally, the factor vector does not have a mean even though the levels are numeric because levels are similar to ranks, whose mean has no numerical meaning. 


## Problem 2
### Data description 
```{r}
data("penguins", package = "palmerpenguins")
penguins
```
The "penguins" dataset contains `r ncol(penguins)` variables and `r nrow(penguins)` subjects. The variables include `r colnames(penguins)`.

```{r}
# mean of flipper with the NA values
mean(pull(penguins,flipper_length_mm))     
# mean of flipper after taking out the NAs
mean(pull(penguins,flipper_length_mm),na.rm = TRUE)
```
The mean of flipper length is unknown, `r mean(pull(penguins,flipper_length_mm))`. This is beacuse there are unknown values in the variable flipper_length_mm

If we take out the unknown values from the flipper_length_mm variable, then the mean of flipper length is `r mean(pull(penguins,flipper_length_mm),na.rm=TRUE)`.

### Scatter plot
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color  = (species))) + geom_point()
ggsave("p8105_hw1_problem2_ym2813.pdf")
```





